---
title: 'Exercises: Chapter 3'
author: "LinMod"
date: "Monday, September 15, 2014"
output:
  pdf_document:
    fig_caption: yes
---

#####3-1

The running proportions plot.

```{r cdf, echo=TRUE}
# Goal: toss a coin N times and get the running proportion of heads
N <- 500
p.heads <- 0.8 # Assume biased coin

# Heads = 1, Tails=0
flipsequence <- sample(x=c(0,1), prob=c(1-p.heads,p.heads), size=N, replace=TRUE) 

r <- cumsum(flipsequence)
n <- 1:N

runprop <- r/n
```

```{r cdf_plot, echo=FALSE, message=FALSE, fig.cap="Running Proportions Plot, # of Heads"}
plot(n, runprop, type="o", ylim=c(0,1), xlim=c(1,N), log='x', ylab="Proportion Heads", xlab="Flip Number", lwd="1", col="blue")
lines(c(1, N), c(p.heads, p.heads), lty=3)
```

\newpage

#####3-2 

Detemine the probability of drawing a 10 from a pinochle deck (9-Ace, 6 of each). 

To do this, we will randomly sample from the deck and see what proportion are tens.

```{r, echo=TRUE}
cards <- c("9", "10", "Jack", "Queen", "King", "Ace")
suits <- c("Hearts", "Diamonds", "Spades", "Clubs")

draws <- cbind.data.frame(sample(cards, size=1000000, replace=TRUE), 
                          sample(suits, size=1000000, replace=TRUE))

length(draws[which(draws[,1]=='10'),1])/length(draws[,1])
length(draws[which(draws[,1]=='10'|draws[,1]=='Jack'),1])/length(draws[,1])
```

Thus, we estimate that the probability of drawing a jack is `r round(length(draws[which(draws[,1]=='10'),1])/length(draws[,1]),3)` and the probability of drawing a 10 or a jack is `r round(length(draws[which(draws[,1]=='10'|draws[,1]=='Jack'),1])/length(draws[,1]),3)`.
