---
title: 'Exercises: Chapter 3'
author: "LinMod"
date: "Monday, September 15, 2014"
output:
  pdf_document:
    fig_caption: yes
---

####3-1

The running proportions plot.

```{r cdf, echo=TRUE}
# Goal: toss a coin N times and get the running proportion of heads
N <- 500
p.heads <- 0.8 # Assume biased coin

# Heads = 1, Tails=0
flipsequence <- sample(x=c(0,1), prob=c(1-p.heads,p.heads), size=N, replace=TRUE) 

r <- cumsum(flipsequence)
n <- 1:N

runprop <- r/n
```

```{r cdf_plot, echo=FALSE, message=FALSE, fig.cap="Running Proportions Plot, # of Heads"}
plot(n, runprop, type="o", ylim=c(0,1), xlim=c(1,N), log='x', ylab="Proportion Heads", xlab="Flip Number", lwd="1", col="blue")
lines(c(1, N), c(p.heads, p.heads), lty=3)
```

\newpage

####3-2 

Detemine the probability of drawing a 10 from a pinochle deck (9-Ace, 6 of each). 

To do this, we will randomly sample from the deck and see what proportion are tens.

```{r, echo=TRUE}
cards <- c("9", "10", "Jack", "Queen", "King", "Ace")
suits <- c("Hearts", "Diamonds", "Spades", "Clubs")

draws <- cbind.data.frame(sample(cards, size=1000000, replace=TRUE), 
                          sample(suits, size=1000000, replace=TRUE))

length(draws[which(draws[,1]=='10'),1])/length(draws[,1])
length(draws[which(draws[,1]=='10'|draws[,1]=='Jack'),1])/length(draws[,1])
```

Thus, we estimate that the probability of drawing a jack is `r round(length(draws[which(draws[,1]=='10'),1])/length(draws[,1]),3)` and the probability of drawing a 10 or a jack is `r round(length(draws[which(draws[,1]=='10'|draws[,1]=='Jack'),1])/length(draws[,1]),3)`.

####3-3

```{r ex3, echo=FALSE, results='asis', message=FALSE, error=FALSE, fig.cap = "PDF - $6x(1-x)$"}

dx <- 0.01
x <- seq(0,1,dx)
y <- 6*x*(1-x)
plot(x, y, type="h", ylab="p(x)", main="Probability Density function", lwd="1")
lines(x,y, lwd="1")
area <- sum(dx*y)
```

From this plot, we estimate that the area underneath the curve is $$\sum^n_ip(x_i)\delta x$$
which is estimated numerically by `R` as `r area`. Analytically, the solution is

$$\int 6x(1-x)\delta x = \int (6x-6x^2)\delta x$$
$$=\int 6x\delta x - \int 6x^2\delta x$$
$$= 3x^2 \vert^1_0 - 2x^3 \vert^1_0$$
$$= (3-2) - (0-0)$$
$$ =1$$

Thus, because the area under the curve is 1, $p(x)$ is a probability density function, and satisfies $Equation 3.3$.

####3-4

#####A)

```{r normal, echo=FALSE}
mean <- 0 # Plot mean value
stdval <- 1 # State standard dev
xlow <- mean - 3*stdval # Determine x low
xhigh <- mean + 3*stdval # Determine higher x lim
dx <- 0.02 # determine small change
x <- seq(xlow, xhigh, dx) # Generate seq of x's
y <- (1/(stdval * sqrt(2*pi))) * exp(-0.5 * ((x-mean)/stdval)^2) # Get y values for each x

plot(x,y, type="h", xlim=c(-3,3))
lines(x,y)
```

This is the distribution $Y \sim N(0,1)$.

#####B)
This statement is essentially that we believe 68% of women will fall within the range of 147cm and 177cm in height, with the average woman's height at 162cm.

####3-5

|       | Ice | Fruit | French Fries|
|-------|---- | ------| ------------|
| 1st   | .25 | 0.6   | 0.125       |
| 6th   | 0.5 | 0.3   | 0.125       |
| 11th  | 0.25| 0.1   | 0.75        |


From this table, which represents $p(grade|snack)$, clearly shows that, given that ice cream is a favorite food, there is a $50\%$ chance that the subject is a 6th grader. Given that fruit is the favorite food, there is a $60\%$ chance that the subject is a 1st grader.  And given that French Fries are the favorite food, there is a $75\%$ that the subject is an 11th grader.  Therefore, we conclude that these probabilities are not independent.