---
title: "Chapter 6 Exercises"
author: "LinMod"
date: "Tuesday, September 23, 2014"
output: pdf_document
---

```{r init, echo=FALSE, cache=TRUE}

source("ch6.R")

```
**6-1**

**A)** The value of `sum(approxMass)` is `r sum(approxMass)`. This is less than 1 because it is not using the analytical solution - instead, this is a numerical approximation of the beta distribution.  

```{r wrong, echo=FALSE}
nIntervals <- 10
width <- 1/nIntervals

theta <- seq(from = 0, to = 1, by=width)

approxMass <- dbeta(theta, 8, 4) * width

ptheta <- approxMass/sum(approxMass)

```


**B)** We cannot use theta on the interval from 0 to 1.  We must use the midpoints.  Using 0 and 1 as endpoints gives an incorrect numerical approximation.  While the widths are the same as the other rectangles, the edges actually extend outside of the beta distribution, giving an over-approximation of the area.  Indeed, using such a parameterization, we see a total probability estimate of `r sum(approxMass)`, which is clearly impossible.

**6-2)** We'll use the example from the book, for ease and convenience (it's late.)

**A)**

```{r prior, echo=TRUE}
ptheta <- c(50:1, rep(1, 50), 1:50)
ptheta <- ptheta/sum(ptheta)

width = 1/length(ptheta)

theta = seq(from=width/2, to=1-width/2, by=width)
```

**B)** Now that we have set the prior, consider the posterior.  

Come back - this will be more worth it tomorrow.
